CODECHECK: An open-science initiative for the independent execution of computations underlying research articles.

### 2021-01-10 codecheck-paper.tex
Naomi okay -- possibly add Emmy?

  \begin{tabular}{llp{11cm}}
    \toprule
    Certificate & Research area & Description \\ \midrule
    2020-001 \cite{cert-2020-001} &
    Machine learning & CODECHECK undertaken post acceptance of
    manuscript and before its publication in \textit{Gigascience}
    \cite{Piccolo2020-lo}. \\
    2020-002  \cite{cert-2020-002} & neuroscience & Paper from 1997
 showing unsupervised learning from natural images \cite{Hancock1992-mp}.
 Code written for this project. \\
    2020-003  \cite{cert-2020-003} & neuroscience &  Classic paper
                                                     from 1982 on
                                                     models of
                                                     associative
                                                     memory
                                                     \cite{Hopfield1982-mz}.
    (Simulation code was written specifically for this project.)\\
    2020-004  \cite{cert-2020-004} & neuroscience & Cart-pole balancing problem solved using reinforcement learning \cite{Barto1983-rg}.  Code written for this reimplementation.\\
    2020-005  \cite{cert-2020-005} & neuroscience & Larisch \\
    2020-006  \cite{cert-2020-006} & neuroscience & Detorakis \\
    2020-007  \cite{cert-2020-007} & neuroscience & \textbf{in progress} \\
    2020-008  \cite{cert-2020-008} & COVID-19 & Modelling of
    interventions on COVID-19 cases in the UK; checked as preprint (NOW REMOVED XXX)
    and now published \cite{Davies2020-vj} \\
    2020-009  \cite{cert-2020-009} & COVID-19 & tracing \\
    2020-010  \cite{cert-2020-010} & COVID-19 & report 9 \\
    2020-011  \cite{cert-2020-011} & COVID-19 & Modelling of Covid
    spread across Europe;  paper was checked when in press (now  published) \cite{Flaxman2020-yb}. \\
    2020-012  \cite{cert-2020-012} & COVID-19 & Modelling of COVID-19 spread across the USA; preprint currently review \cite{Unwin2020}. \\
    2020-013  \cite{cert-2020-013} & neuroscience & biorXiv \cite{Spitschan2020.06.02.129502}. \\
    2020-014  \cite{cert-2020-014} & neuroscience & eLife \cite{Sadeh2020}. \\
    2020-015  \cite{cert-2020-015} & neuroscience & eLife \cite{Liou2020}. \\
    2020-016  \cite{cert-2020-016} & GIScience & 
    R models demonstrating the Modifiable Aral Unit Problem (MAUP) in spatial data science \cite{Brunsdon2020}. \\
    2020-017  \cite{cert-2020-017} & GIScience & 
    Spatial data handling, analysis, and visualisation using a variety of R packages \cite{Bivand2020}. \\
    2020-018  \cite{cert-2020-018} & GIScience & 
    Cellular automaton in R for modeling dynamic phenomena within a Discrete Global Grid System (DGGS) data model; using a subset for demonstration \cite{Hojati2020}. \\
    2020-019  \cite{cert-2020-019} & GIScience & Reachability analysis of suburban transportation using analysis of privately owned shared cars; workflow uses Python, and reproduction with a considerably subsampled dataset \cite{Illium2020}. \\
    2020-020  \cite{cert-2020-020} & GIScience & In-database windows operators for processing spatio-temporal data streams based on Python and PostgreSQL/PostGIS \cite{Werner2020}; reproduction using container. \\
    2020-021  \cite{cert-2020-021} & GIScience & Python code for comparing supervised machine learning models for spatial nominal entity recognition. \cite{Medad2020}. \\
    2020-022  \cite{cert-2020-022} & GIScience & Python code for visualising text analysis on intents and concepts from geo-analytic questions \cite{Xu2020}. \\
    2020-023  \cite{cert-2020-023} & GIScience & Analysis of spatial footprints of geo-tagged extreme weather events from social media using R \cite{Owuor2020}. \\
    \\ \bottomrule
  \end{tabular}
  \caption{Register of completed certificates as of October 2020.  An interactive version
  is available at \url{http://codecheck.org.uk/register}. % TODO: SJE to complete...
  }
  \label{tab:register}
\end{table}

@@

% question mark indicates we are waiting for person to respond.
We are grateful to the following individuals for discussions regarding
the work presented here: Andy Collings, Melissa Harrison?, Giuliano
Maciocci, Naomi Penfold? (eLife), Rebecca Kirk (PLOS Computational Biology), Scott
Edmunds (GigaScience), and Andrew Hufton? (Scientific Data). Iain Davies and
Yuhao (Sebastian) Wang developed code and example certificates.
We thank Antonio P\'{a}ez? (Journal of Geographical Systems) for enabling
CODECHECKs, Carlos Granell and Frank Ostermann? for contributing
certificates as reproducibility reviewers at the AGILE conference, and 
all authors of auditable workflows for their participation.

>>>>

  \begin{tabular}{llp{11cm}}
    \toprule
    Certificate & Research area & Description \\ \midrule
    2020-001 \cite{cert-2020-001} &
    Machine learning & CODECHECK undertaken post acceptance of
    manuscript and before its publication in \textit{Gigascience}
    \cite{Piccolo2020-lo}. \\
    2020-002  \cite{cert-2020-002} & neuroscience & Paper from 1997
 showing unsupervised learning from natural images \cite{Hancock1992-mp}.
 Code written for this project. \\
    2020-003  \cite{cert-2020-003} & neuroscience &  Classic paper
                                                     from 1982 on
                                                     models of
                                                     associative
                                                     memory
                                                     \cite{Hopfield1982-mz}.
    (Simulation code was written specifically for this project.)\\
    2020-004  \cite{cert-2020-004} & neuroscience & Cart-pole balancing problem solved using reinforcement learning \cite{Barto1983-rg}.  Code written for this reimplementation.\\
    2020-005  \cite{cert-2020-005} & neuroscience & Larisch \\
    2020-006  \cite{cert-2020-006} & neuroscience & Detorakis \\
    2020-007  \cite{cert-2020-007} & neuroscience & \textbf{in progress} \\
    2020-008  \cite{cert-2020-008} & COVID-19 & Modelling of
    interventions on COVID-19 cases in the UK; checked as preprint
    and now published \cite{Davies2020-vj} \\
    2020-009  \cite{cert-2020-009} & COVID-19 & tracing \\
    2020-010  \cite{cert-2020-010} & COVID-19 & report 9 \\
    2020-011  \cite{cert-2020-011} & COVID-19 & Modelling of Covid
    spread across Europe;  paper was checked when in press (now  published) \cite{Flaxman2020-yb}. \\
    2020-012  \cite{cert-2020-012} & COVID-19 & Modelling of COVID-19 spread across the USA; preprint currently review \cite{Unwin2020}. \\
    2020-013  \cite{cert-2020-013} & neuroscience & biorXiv \cite{Spitschan2020.06.02.129502}. \\
    2020-014  \cite{cert-2020-014} & neuroscience & eLife \cite{Sadeh2020}. \\
    2020-015  \cite{cert-2020-015} & neuroscience & eLife \cite{Liou2020}. \\
    2020-016  \cite{cert-2020-016} & GIScience & 
    R models demonstrating the Modifiable Aral Unit Problem (MAUP) in spatial data science \cite{Brunsdon2020}. \\
    2020-017  \cite{cert-2020-017} & GIScience & 
    Spatial data handling, analysis, and visualisation using a variety of R packages \cite{Bivand2020}. \\
    2020-018  \cite{cert-2020-018} & GIScience & 
    Cellular automaton in R for modeling dynamic phenomena within a Discrete Global Grid System (DGGS) data model; using a subset for demonstration \cite{Hojati2020}. \\
    2020-019  \cite{cert-2020-019} & GIScience & Reachability analysis of suburban transportation using analysis of privately owned shared cars; workflow uses Python, and reproduction with a considerably subsampled dataset \cite{Illium2020}. \\
    2020-020  \cite{cert-2020-020} & GIScience & In-database windows operators for processing spatio-temporal data streams based on Python and PostgreSQL/PostGIS \cite{Werner2020}; reproduction using container. \\
    2020-021  \cite{cert-2020-021} & GIScience & Python code for comparing supervised machine learning models for spatial nominal entity recognition. \cite{Medad2020}. \\
    2020-022  \cite{cert-2020-022} & GIScience & Python code for visualising text analysis on intents and concepts from geo-analytic questions \cite{Xu2020}. \\
    2020-023  \cite{cert-2020-023} & GIScience & Analysis of spatial footprints of geo-tagged extreme weather events from social media using R \cite{Owuor2020}. \\
    \\ \bottomrule
  \end{tabular}
  \caption{Register of completed certificates as of October 2020.  An interactive version
  is available at \url{http://codecheck.org.uk/register}. % TODO: SJE to complete...
  }
  \label{tab:register}
\end{table}

@@

% question mark indicates we are waiting for person to respond.
We are grateful to the following individuals for discussions regarding
the work presented here: Andy Collings, Melissa Harrison?, Giuliano
Maciocci, Naomi Penfold, Emmy Tsang? (eLife), Rebecca Kirk (PLOS
Computational Biology), Scott Edmunds (GigaScience), and Andrew
Hufton? (Scientific Data). Iain Davies and Yuhao (Sebastian) Wang
developed code and example certificates.  We thank Antonio P\'{a}ez?
(Journal of Geographical Systems) for enabling CODECHECKs, Carlos
Granell and Frank Ostermann? for contributing certificates as
reproducibility reviewers at the AGILE conference, and all authors of
auditable workflows for their participation.
